Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-02 src/article.tex
Add version to requirements
Revise conclusions

  \begin{description}
    \item[Project name:] Scaffolder, version 0.4.1
    \item[Project home page:] \scaffolder
    \item[Operating system:] Platform Independent. Tested on Mac OS X and
    Debian.
    \item[Programming language:] Ruby
    \item[Other requirements:] RubyGems
    \item[License:] MIT
    \item[Any restrictions to use by non-academics:] None
  \end{description}

@@

An example scaffold file written using the YAML syntax \cite{yaml} (left) and
the resulting putative scaffold (right). The scaffold contains three entries
and two inserts. Each entry in the scaffold file text is delimited by a `-' on
a new line and highlighted using separate colours. The scaffold diagram on the
right is not to scale but illustrates how the scaffold sequences are joined.
\pb

>>>>

  \begin{description}
    \item[Project name:] Scaffolder v0.4.1, Scaffolder Tools v0.1.2
    \item[Project home page:] \scaffolder
    \item[Operating system:] Platform Independent. Tested on Mac OS X and
    Debian.
    \item[Programming language:] Ruby
    \item[Other requirements:] RubyGems
    \item[License:] MIT
    \item[Any restrictions to use by non-academics:] None
  \end{description}

@@

An example scaffold file written using the YAML syntax \cite{yaml} (left) and
the resulting putative scaffold sequence (right). The scaffold contains three
entries and two inserts. Each entry in the scaffold file text is delimited by
a `-' on a new line and highlighted using separate colours. The scaffold
diagram on the right is not to scale and instead illustrates how the scaffold
sequences are joined. \pb
